Create data sets for modeling

### 2016-07-30 portfolio/analysis/3-createData_linear_modeling.Rmd
messing around with additional output / vars

cfecAnnual = group_by(cfecnew, p_holder, year) %>%
  summarize(permit = p_fshy[1], boat = cadfg[1],
    days = diff(range(yday) + 1),
    days_n = length(unique(yday)),
    days_permit = tot.permitDays[1], 
    ngear = length(unique(gearn)),
    nspec = length(unique(specn)),
    npermit = length(unique(p_fshy)),
    revenue = sum(g_earn),
    weight = sum(g_pounds),
    length = mean(vlength, na.rm=TRUE),
    strategy = strategy[1],
    strategy_gear = strategy_gear[1],
    strategy_permit = strategy.permit[1])

@@

cfecAnnual$permit.prev = cfecAnnual$permit[idx]
cfecAnnual$ngear.prev = cfecAnnual$ngear[idx]
cfecAnnual$nspec.prev = cfecAnnual$nspec[idx]
cfecAnnual$npermit.prev = cfecAnnual$npermit[idx]
cfecAnnual$revenue.prev = cfecAnnual$revenue[idx]
cfecAnnual$specdiv.prev = cfecAnnual$specDiv[idx]
cfecAnnual$geardiv.prev = cfecAnnual$gearDiv[idx]
cfecAnnual$strategy.prev = cfecAnnual$strategy[idx]
cfecAnnual$strategy_gear.prev = cfecAnnual$strategy_gear[idx]
cfecAnnual$strategy_permit.prev = cfecAnnual$strategy_permit[idx]
cfecAnnual$weight.prev = cfecAnnual$weight[idx]
cfecAnnual$days.prev = cfecAnnual$days[idx]
```

>>>>

cfecAnnual = group_by(cfecnew, p_holder, year) %>%
  summarize(permit = p_fshy[1], boat = cadfg[1],
    days = diff(range(yday) + 1),
    days_n = length(unique(yday)),
    days_permit = tot.permitDays[1], 
    ngear = length(unique(gearn)),
    nspec = length(unique(specn)),
    npermit = length(unique(p_fshy)),
    revenue = sum(g_earn),
    weight = sum(g_pounds),
    length = mean(vlength, na.rm=TRUE),
    strategy = strategy[1],
    strategy_gear = strategy_gear[1],
    strategy_permit = strategy.permit[1],
    chnk = sum(g_earn[spec=="CHNK"]),
    coho = sum(g_earn[spec=="COHO"]),
    pink = sum(g_earn[spec=="PINK"]),
    sock = sum(g_earn[spec=="SOCK"]),
    chum = sum(g_earn[spec=="CHUM"]))

@@

cfecAnnual$permit.prev = cfecAnnual$permit[idx]
cfecAnnual$ngear.prev = cfecAnnual$ngear[idx]
cfecAnnual$nspec.prev = cfecAnnual$nspec[idx]
cfecAnnual$npermit.prev = cfecAnnual$npermit[idx]
cfecAnnual$revenue.prev = cfecAnnual$revenue[idx]
cfecAnnual$specdiv.prev = cfecAnnual$specDiv[idx]
cfecAnnual$geardiv.prev = cfecAnnual$gearDiv[idx]
cfecAnnual$strategy.prev = cfecAnnual$strategy[idx]
cfecAnnual$strategy_gear.prev = cfecAnnual$strategy_gear[idx]
cfecAnnual$strategy_permit.prev = cfecAnnual$strategy_permit[idx]
cfecAnnual$weight.prev = cfecAnnual$weight[idx]
cfecAnnual$days.prev = cfecAnnual$days[idx]
cfecAnnual$days_permit.prev = cfecAnnual$days_permit[idx]
cfecAnnual$chnk.prev = cfecAnnual$chnk[idx]
cfecAnnual$coho.prev = cfecAnnual$coho[idx]
cfecAnnual$chum.prev = cfecAnnual$chum[idx]
cfecAnnual$pink.prev = cfecAnnual$pink[idx]
cfecAnnual$sock.prev = cfecAnnual$sock[idx]
```
